Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-02-06 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-body.tex
Abstract and new Image

Moreover, modeling the performance of an C-IEC system
involves understanding its dynamics. Previous works on browser-based
volunteer computing have used basic metrics such as
the number of users or the time spent by every one in the
computation \cite{DBLP:journals/gpem/LaredoBGVAGF14, 2016arXiv160101607M}. 
While works on other platforms such as SETI@home
\cite{javadi2009mining} have found that the Weibull, log-normal, and
Gamma distributions where viable models of the  
the availability of computing resources in several clusters, which  is 
in concordance with the results obtained in \cite{agajaj}, and also
browser-based volunteer evolutionary systems like NodIO \cite{DBLP:conf/gecco/MereloCGCRV16}.
The shape of those distributions is a skewed bell
with more resources in the {\em low} areas than in the high areas; i.e., 
there are many users that give a small amount of cycles, while there
are just a few that give many cycles. In order to assess gamification techniques alongside C-IEC follows the
same pattern, participation was flitted to a 
Weibull distribution,
and shown in Figures \ref{fig:w2} and \ref{fig:w3}, 
confirming  this model for user interaction, although with different fitted
values in each case. 
%
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/weibull_2.png}
    \caption{Experiment G. Weibull Fit}
    \label{fig:w2}
\end{figure}
%
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/weibull_3.png}
    \caption{Experiment GG. Weibull Fit}
    \label{fig:w3}
\end{figure}

\section{Case Study: EvoDraw-Kinect}
\label{sec:kinect}
A variation of the previous application is The EvoDraw installation, using the same
framework but with a different form of interaction. Humans interact with the animations 
by simply looking at them. Again the population is stored in the EvoSpace container and
client computers remove animations from the EvoSpace to be presented in a display one at a time. 
After a certain amount of time,  animations are put back to the server along with information 
generated from the interaction. To continue, another is again removed and presented to viewers. 
This cycle continues until there is enough interactions to create a new generation of animations.

In order to assign a fitness value to each animation and thus enabling 
the EA the selection of the most interesting animations, a natural user interface 
device (Kinect sensor for Xbox One) is used for facial tracking. Each animation is 
presented several times in a single generation and the best are always passed to the next, 
with its fitness recomputed. To generate the new population the same operators as the previous case study
are applied to the population.

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.3in]{img/kinect.png}
    \caption{EvoDraw Installation on ------ -- --- ----.}
    \label{fig:kinect}
\end{figure}

In this installation the components of the framework used where EvoSpace and the EA.
Information from users was limited to a stream of readings from the
sensor.
% This has nothing to do with the rest of the paper. You are not
% modeling anything. It's just another application of the
% framework. Could be mentioned in the state of the art, that's
% all. We should devote more space to the study of user interactions.

\section{Case Study: XYZ-Unplugged}
\label{sec:xyz}

XYZ is a collective artwork generated by means of the Unplugged version of the EA \cite{de2014artists}.
While in the previous cases interactive tools are in charge of running the EA and users collaborate evaluating
fitness quality, the proposed framework in XYZ is mainly in charge of storing digital versions of the works produced 
by the team of artists, who are really in charge of applying every step of the EA. Thus the team of artists 
are in charge of:  (i) setting up the initial population by selecting in the web interface
well known works from the history of arts;  (ii) each of the artists selects, every generation, two works 
from the previous one (see Figure \ref{fig:xyz}), and produce a new painting by applying 
any kind of crossover and mutation he or she may consider  (iii) the process repeats for the number 
of generations initially decided, so that at the end, a collective  artwork has been produced 
including as many paintings per generation, as artists are participating in the experiment. In this application
the final product is the motivation.

Artists resort to the framework as the tool allowing them 
to store the paintings, deciding their preferred ones from the
previous generation, as well as describing the reasons for their 
selections, mutation and crossover operations applied.
The tool is also in charge of generating statistics, 
computing \textit{elitism}, thus adding the most selected work to 
the next generation, etc.

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/interfaceXYZ.png}
    \caption{User interface of the XYZ application, used by artists to select the best pair of the current generation.}
    \label{fig:xyz}
\end{figure}
% Once again, no model, no relation to the rest of the paper. Either
% you talk about a model of interactions with humans and their
% similarity with the first case study, or you eliminate it. How do
% you tackle boredom? How do you increase engagement? Those are the
% paper's topics, you can't just drop it here because it's interactive
% - JJ

>>>>

Moreover, modeling the performance of an C-IEC system
involves understanding its dynamics. Previous works on browser-based
volunteer computing have used basic metrics such as
the number of users or the time spent by every one in the
computation \cite{DBLP:journals/gpem/LaredoBGVAGF14, 2016arXiv160101607M}. 
While works on other platforms such as SETI@home
\cite{javadi2009mining} have found that the Weibull, log-normal, and
Gamma distributions where viable models of the  
the availability of computing resources in several clusters, which  is 
in concordance with the results obtained in \cite{agajaj}, and also
browser-based volunteer evolutionary systems like NodIO \cite{DBLP:conf/gecco/MereloCGCRV16}.
The shape of those distributions is a skewed bell
with more resources in the {\em low} areas than in the high areas; i.e., 
there are many users that give a small amount of cycles, while there
are just a few that give many cycles. In order to assess gamification techniques alongside C-IEC follows the
same pattern, participation was flitted to a 
Weibull distribution,
and shown in Figures \ref{fig:w1} and \ref{fig:w3}, 
confirming  this model for user interaction, although with different fitted
values in each case. 
%
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/weibull_1.png}
    \caption{Deployment B. Weibull Fit.}
    \label{fig:w1}
\end{figure}
%
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/weibull_2.png}
    \caption{Deployment G. Weibull Fit.}
    \label{fig:w2}
\end{figure}

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/weibull_3.png}
    \caption{Deployment GG. Weibull Fit.}
    \label{fig:w3}
\end{figure}

% This has nothing to do with the rest of the paper. You are not
% modeling anything. It's just another application of the
% framework. Could be mentioned in the state of the art, that's
% all. We should devote more space to the study of user interactions.

% Once again, no model, no relation to the rest of the paper. Either
% you talk about a model of interactions with humans and their
% similarity with the first case study, or you eliminate it. How do
% you tackle boredom? How do you increase engagement? Those are the
% paper's topics, you can't just drop it here because it's interactive
% - JJ

### 2017-02-06 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-front.tex
Abstract and new Image

\begin{abstract}
The necessary intervention of humans in interactive evolutionary
computational systems has inherent drawbacks arising from the very nature of 
the algorithms, namely, the human fatigue caused by the interaction, and
the boredom arising when users evaluate a large number of artifacts.
To tackle these issues, in this paper we
propose a human-centered framework to modelthe complex interactions on these systems.
Three case studies are presented where the model is applied in the 
development of evolutionary interactive systems, with different techniques:
volunteer-collaborative, unplugged and sensor-based. 
Both conceptual and implementation details are provided where the   
technique is applied to measure and increase user engagement and participation.
Our experiments show that the model can be successfully applied in a
gamification technique developed to increase user engagement, which
implies that this technique can successfully be used to 
decrease user fatigue and thus increase {\em performance} of the
interactive system.
\end{abstract}

>>>>

\begin{abstract}
The necessary intervention of humans in interactive evolutionary
computational systems has inherent drawbacks arising from the very nature of 
the algorithms, namely, the human fatigue caused by the interaction, and
the boredom arising when users evaluate a large number of artifacts.
To tackle these issues, in this paper we
propose a human-centered framework to model the complex interactions 
found on these systems.
A case study is presented, providing both conceptual and implementation 
details where the model is applied to measure and increase user engagement and participation
in a collaborative, volunteer based, evolutionary interactive system. 
Our experiment shows that the model can be successfully applied for developing a
gamification technique to increase user engagement, which
implies that this technique can successfully be used to 
decrease user fatigue and boredom, and thus increase the {\em performance} of the
interactive system.
\end{abstract}
